Code for Graphs for ASN presentation

### 2021-03-15 ASNCodeUpdatedFigs.Rmd
Got second graph, saved versions of the graphs as images

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = food, shape = fate), 
       data = datameans) + 
  theme_bw() + 
  ylim(0, 20) + 
  xlim(15, 45) +
  geom_point(size = 3) + 
  scale_shape_manual(values = c(5, 2, 1, 19)) + 
  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
  geom_errorbarh(aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
  guides(size = FALSE) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Developmental Outcome", color = "Hostplant Consumed")
```

>>>>

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = food, shape = fate), 
       data = datameans) + 
  theme_bw() + 
  ylim(0, 20) + 
  xlim(15, 45) +
  geom_point(size = 4) + 
  scale_shape_manual(values = c(5, 2, 1, 19)) + 
  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
  geom_errorbarh(aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
  guides(size = FALSE) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Developmental Outcome", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/meantime.png", width = 8, height = 5)
```

```{r}
ggplot(aes(x = area, y = mass.max, color = food, shape = fate), 
       data = datameans) + 
  theme_bw() + 
  ylim(0, 20) + 
  xlim(0, 6000) +
  geom_point(size = 4) + 
  scale_shape_manual(values = c(5, 2, 1, 19)) + 
  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
  geom_errorbarh(aes(xmin = area - searea, xmax = area + searea), size = .5) + 
  guides(size = FALSE) + 
  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (g)", 
       shape = "Developmental Outcome", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/meanarea.png", width = 8, height = 5)
```
